Embedding Dimension of Polyhedral Losses

### 2020-01-31 colt-20/embed-dim.tex
Adding example of real-valued embedding

  Let $\gamma:\simplex\toto\R$ be finite and monotone.
  Then we can use the total ordering of $\R$ to write $\R = \{r_1,\ldots,r_k\}$ such that $r_i < r_{i+1}$ for all $i \in \{1,\ldots,k-1\}$.
  We now have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{a(r_{i+1})}{p} \leq 0 \leq \inprod{b(r_i)}{p} \}$.
  If this intersection is empty, then there must be some $p$ with $\inprod{b(r_i)}{p} < 0$ and $\inprod{a(r_{i+1})}{p} > 0$; by monotonicity, no earlier or later reports can be in $\gamma(p)$, so we see that $\gamma(p) = \emptyset$, a contradiction.
  Thus the intersection is nonempty, and as we also know $b(r_i) \leq a(r_{i+1})$ we conclude $b(r_i) = a(r_{i+1})$, and the intersection is the hyperplane defined by $b(r_i) = a(r_{i+1})$.

\end{proof}

>>>>

  Let $\gamma:\simplex\toto\R$ be finite and monotone.
  Then we can use the total ordering of $\R$ to write $\R = \{r_1,\ldots,r_k\}$ such that $r_i < r_{i+1}$ for all $i \in \{1,\ldots,k-1\}$.
  We now have $\gamma_{r_i} \cap \gamma_{r_{i+1}} = \{p\in\simplex : \inprod{a(r_{i+1})}{p} \leq 0 \leq \inprod{b(r_i)}{p} \}$.
  If this intersection is empty, then there must be some $p$ with $\inprod{b(r_i)}{p} < 0$ and $\inprod{a(r_{i+1})}{p} > 0$; by monotonicity, no earlier or later reports can be in $\gamma(p)$, so we see that $\gamma(p) = \emptyset$, a contradiction.
  Thus the intersection is nonempty, and as we also know $b(r_i) \leq a(r_{i+1})$ we conclude $b(r_i) = a(r_{i+1})$, and the intersection is the hyperplane defined by $b(r_i) = a(r_{i+1})$.
\end{proof}

\subsection{Example construction of real-valued embedding}
For concreteness, let us now construct an embedding via the loss given in Theorem~\ref{thm:construct-1d-loss}.
We start with the discrete loss given in Table~\ref{tab:example-orderable}

\begin{center}
\begin{tabular}{c|cc|}	\label{tab:example-orderable}
	& $y_1$& $y_2$ \\ \hline
	$r_1$ & 5 & 3 \\
	$r_2$ & 4 & 1 \\
	$r_3$ & 2 & 1 \\
	$r_4$ & 1 & 4 \\
	$r_5$ & 1 & 6 \\
	$r_6$ & 3 & 8 \\
\end{tabular}
\captionof{table}{Ordered discrete loss that we embed.}
\end{center}

Given this loss, we can calculate $v(i)_y$ for both losses, shown by the \textbullet $\;$ in Figure~\ref{fig:real-embed-vs}.

Note here that we observe $K = 4$, $\Lambda = (1, 1/2, 1/2, 3/4, 3/4)$, and embedding points $\varphi(\R) = (0,1,3,5, 19/3, 23/3)$.
The polyhedral loss is then shown in Figure~\ref{fig:real-embed-loss}.

\begin{figure}
	\begin{minipage}{0.45\linewidth}
	\centering
	\includegraphics[width=0.7\linewidth]{tikz/real-embed-vs}
	\caption{\textbullet $\;$ represents the original $v_i$, where blue is used for $v(\cdot)_{y_1}$ and red for $v(\cdot)_{y_2}$.  The $\times$ symbol of the same color is the $\Lambda$-corrected directional derivative to force monotonicity.}
	\label{fig:real-embed-vs}	
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
	\centering
	\includegraphics[width=0.7\linewidth]{tikz/real-embed-loss}
	\caption{Our constructed embedding $L$ for the discrete loss $\ell$ given in Table~\ref{tab:example-orderable}.}
	\label{fig:real-embed-loss}
\end{minipage}
\end{figure}

\jessie{If time, write out symbolic calculation}
